### 2014-06-27 alex/school_poverty.Rmd

```{r competition}
comp = school2012 %>% 
  select(CNT, SCHOOLID, SC04Q01) %>% 
  group_by(CNT) %>%
  summarise(other = 
              sum(SC04Q01 == "Two or More", na.rm=T) / length(CNT)) %>% 
  arrange(desc(other)) %>%
   left_join(
    student2012.sub %>% group_by(CNT) %>% summarise(m_math = mean(math))
  )

@@

>>>>

Competition between schools
```{r competition}
comp = school2012 %>% 
  select(CNT, SCHOOLID, SC04Q01) %>% 
  group_by(CNT) %>%
  summarise(other = 
              sum(SC04Q01 == "Two or More", na.rm=T) / length(CNT)) %>% 
  arrange(desc(other)) %>%
   left_join(
    student2012.sub %>% group_by(CNT) %>% summarise(m_math = mean(math))
  )

@@

Math teacher shortages
```{r shortages}
school2012.sub = school2012 %>% select(CNT, SCHOOLID, SC11Q02, SC11Q03, SC14Q02, SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11, SC14Q12, SC14Q13)
student2012.sub = student2012 %>% select(CNT, SCHOOLID, math, read, sci)
school2012.sub = fix_country(school2012.sub)
student2012.sub = fix_country(student2012.sub)

scores_by_school = student2012.sub %>% group_by(CNT, SCHOOLID) %>% summarise(mmath = mean(math), mread = mean(read), msci = mean(sci))

df = scores_by_school %>% left_join(school2012.sub)
qplot(SC14Q02, mmath2, data = df %>% group_by(CNT, SC14Q02) %>% summarise(mmath2 = mean(mmath)), facets = ~CNT)
qplot(SC14Q10, mmath2, data = df %>% group_by(CNT, SC14Q10) %>% summarise(mmath2 = mean(mmath)), facets = ~CNT)
```

looking at just the US
```{r shortages1}
library(ggplot2)
qplot(SC14Q02, mmath, data = df %>% group_by(CNT, SC14Q02) %>% 
        filter(CNT == "United States of America"), geom="boxplot")
```

```{r shortages2}
library(ggplot2)
df2 = df%>% select(CNT, SCHOOLID, mmath, mread, msci, SC14Q02,
                  SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11,
                  SC14Q12, SC14Q13)
for(i in 6:13) {
  df2[,i] = as.numeric(df2[,i])
}

df2$sum = apply(df2[,6:13], 1, sum, na.rm=T)
qplot(x = sum, y = m2, data = df2 %>% group_by(CNT, sum) %>% summarise(m2 = mean(mmath)), facets=~CNT)

qplot(x = pSC14Q07, mmath2, data = 
df2 %>% group_by(CNT) %>% 
  summarise(pSC14Q07 = sum(SC14Q07 == 4, na.rm=T) / length(CNT),
            mmath2 = mean(mmath)) %>% 
  arrange(pSC14Q07)
)
```
